---
title: "Shiny Application and Reproducible Pitch"
author: "Francesco Canuto"
date: "30 maggio 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
```

## Overview

This peer assessed assignment has two parts. First, creation of a Shiny application and deployment on Rstudio's servers. Second, a Rstudio presentation about your application.

The shiny application is available [here](https://noldem.shinyapps.io/myApp/)

The github repository with source code is available [here](https://github.com/FrancescoCanuto/shinyapp)

## Application descritption

Tha application is developed using shiny. It provides the annual cost of owneship of a selecting some car features.

First, it requires you provide an estimation of your mileage per year [Milage per year input box] and the cost of fuel [Dollars per gallon].

Second, you have to input power of your vehicle [Engine Power]

Selction of type of transmission [Type of transmission] and Type of engine] are optional and not mandatory

As soon you have inputed your data, a regression model estimate your mpg (black point in the chart) and estimate total cost of ownership per year.

## mtcars dataset

The dataset is the Motor Trend Car Road Tests present in R
```{r cars, echo = TRUE}
head(mtcars)
```

## the plot

The regression model with mpg estimation
```{r pressure}
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- as.factor(mtcars$am)
plot <- ggplot(data=mtcars, aes(x=hp, y = mpg))+
            geom_point(aes(color = cyl), alpha = 0.6)+
            geom_smooth(method = "lm")+
            geom_point(x=150, y=20, size=5) +
            annotate("text", x=150+20, y=20+1, label="mpg: 20.00")
        plot
```

